Simulating physiological flexibility in the acute glucocorticoid response to stressors reveals limitations of current empirical approaches

### 2022-06-30 3_r_scripts/Manuscript.Rmd
Working on revision.

     p1 <- ggplot(comp_sim2, mapping = aes(x = time, y = cort, by = animal_sample, color = type)) +
       geom_line(alpha = 0.3, size = 0.7) +
       theme_classic() +
       coord_cartesian(xlim = c(0, 60), ylim = c(0, 75)) +
       xlab("Time (minutes)") + ylab("Corticosterone (ng/\U00B5l)") +
       scale_color_manual(values = c("slateblue", "orange")) +
       #guides(color = "none") +
       theme(axis.title = element_text(size = 14)) +
       annotate(geom = "text", x = -Inf, y = Inf, hjust = -.5, vjust = 1.5, label = "A") +
       geom_smooth(se = FALSE, size = 1.5, mapping = aes(by = type, color = type)) +
       theme(legend.title = element_blank())

>>>>

     p1 <- ggplot(comp_sim2, mapping = aes(x = time, y = cort, by = animal_sample, color = type)) +
       geom_line(alpha = 0.3, size = 0.7) +
       theme_classic() +
       coord_cartesian(xlim = c(0, 60), ylim = c(0, 75)) +
       xlab("Time (minutes)") + ylab("Corticosterone (ng/\U00B5l)") +
       scale_color_manual(values = c("#9D93DE", "#FDAE42")) +
       #guides(color = "none") +
       theme(axis.title = element_text(size = 14)) +
       annotate(geom = "text", x = -Inf, y = Inf, hjust = -.5, vjust = 1.5, label = "A") +
       geom_smooth(se = FALSE, size = 1.5, mapping = aes(by = type, color = type)) +
       theme(legend.title = element_blank())
